---
title: "Practice SG MLR"
author: "Ahmad Firdaus Mohamed"
date: "2024-01-21"
output: word_document
---

# 1. Data were collected to study factors that were related with HbA1c. The dataset is named as “metab_syndrome” and in .xlsx formats. (FIRDAUS) (? Dataset [https://github.com/drkamarul/multivar_data_analysis/blob/main/data/metabolic_syndrome.dta)](https://github.com/drkamarul/multivar_data_analysis/blob/main/data/metabolic_syndrome.dta))

A model was proposed to examine the relationship between HBA1C with these covariates: AGE, DMDX, MSBPR, FBS and HDL.

a\. Write the regression model and equation for MODEL_A. (15 marks)

# Prepare Environment

## Load Library

```{r}
library(tidyverse)
library(broom)
library(ggplot2)
library(corrplot)
library(gtsummary)
library(haven)
```

## Read Data

```{r}
Data1<-read_dta("metabolic_syndrome.dta")
summary(Data1)
```

## Select relevant variables

```{r}
Data2 <- Data1 %>%
  select(hba1c,age,dmdx,msbpr,fbs,hdl,mdbpr)
```

Clear NA data

```{r}
Data2 <- Data2 %>%
  na.omit()
```

```{r}
summary(Data2)
```

```{r}
Data2 <- Data2 %>%
  mutate(dmdx = as_factor(dmdx))
```

```{r}
summary(Data2)
```

## Model A

```{r}
MODEL_A <- lm (hba1c~age + dmdx + msbpr + fbs + hdl, data = Data2 )
summary(MODEL_A)
```

```{r}
tidy(MODEL_A, conf.int = TRUE)
```

## Regression Model & Equation

hba1c = 3.77 + 1.34 (dmdxyes) + 0.32 (fbs)

```         
Adjusted R-squared:  0.5455 
```

# b. Add variable MDBPR to MODEL_A and name the new model as MODEL_B. Describe the effect of this addition to the model. (5 marks)

```{r}
MODEL_B <- lm (hba1c ~ age + dmdx + fbs + hdl + msbpr + mdbpr, data = Data2)
summary (MODEL_B)
```

```         
Adjusted R-squared:  0.5478 
```

By adding mdbpr into the model, the model is able to predict the hba1c better from 54.55 % to 54.78%

# c. Perform comparison between MODEL_A and MODEL_B. Give comment. (5 marks)

```{r}
anova (MODEL_A, MODEL_B)
```

The p-value is \<0.001, hence the re is significant difference between the models

# d. Perform model assessment for MODEL_B. Save the relevant plots in the thumb-drive and write the names of the plots in the answer sheet. (10 marks).

```{r}
plot(MODEL_B)
```

```{r}
library(lmtest)
```

```{r}
bptest(MODEL_B)
```

p-value is \<0.005, hence assumption of equal residual variance is violated

```{r}
shapiro.test(MODEL_B$residuals)
```

p-value is \<0.005, hence assumption of normality of residual is violated

# e. Predict the average value of HBA1C for a population with:

AGE = 48 years

DMDX = has history of diabetes (1)

MSBPR = 133 mmHg

MDBPR = 79 mmHg

FBS = 5.6 mmol/l

HDL = 1.3 mmol/l

Show your calculation. (5 marks)

```{r}
summary(MODEL_B)
```

equation

hba1c = 3.49 + 1.33 (dmdxyes) + 0.31 (fbs)

```{r}
summary(model.matrix(MODEL_B))
```

To predict by coding

```{r}
predict(MODEL_B, list(age=48, dmdx="yes", msbpr=133, mdbpr=79, hdl=1.3, fbs=5.6 ))
```

To predict manually by equation

hba1c = 3.49 + 1.33 (dmdxyes) + 0.31 (fbs)

```{r}
3.49 + (1.33 *1) + (0.31 *5.6)
```

AGE = 48 years

DMDX = has history of diabetes (1)

MSBPR = 133 mmHg

MDBPR = 79 mmHg

FBS = 5.6 mmol/l

HDL = 1.3 mmol/l
