---
title: "Practice SG MLR"
author: "Ahmad Firdaus Mohamed"
date: "2024-01-21"
output: word_document
---

# Prepare Environment

## Load Library

```{r}
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(haven)
library(corrplot)
library(tidyr)
```

## Read Data

```{r}
Data1<-read_dta("metabolic_syndrome.dta")
summary(Data1)
```

```{r}
Data2<-select(Data1,hba1c,age,dmdx,msbpr,fbs,hdl,mdbpr)
summary(Data2)
```

### Mutate dmdx to categorical

```{r}
Data2<- Data2 %>%
  mutate(dmdx= as_factor(dmdx))
```

```{r}
summary(Data2)
```

### Remove missing data

```{r}
Data2 <- Data2 %>%
  na.omit()
```

```{r}
summary(Data2)
```

### Summary in Table

```{r}
Descriptive.tbl<- tbl_summary(statistic=list(all_continuous()~"{mean}({sd})", all_categorical()~"{n}/{N} ({p}%)"),Data2)
Descriptive.tbl
```

## Explore Data

Histogram for numerical & barplot for categorical

Numerical age,msbpr,fbs,hdl,mdbpr

Categorical dmdx

### hba1c

```{r}
Data2 %>%
  ggplot(aes(hba1c)) + geom_histogram()
```

### age

```{r}
Data2 %>%
  ggplot(aes(age)) + geom_histogram()
```

### msbpr

```{r}
Data2 %>%
  ggplot(aes(msbpr))+geom_histogram()
```

### fbs

```{r}
Data2 %>%
  ggplot(aes(fbs))+geom_histogram()
```

### hdl

```{r}
Data2 %>%
  ggplot(aes(hdl))+geom_histogram()
```

### mdbpr

```{r}
Data2 %>%
  ggplot(aes(mdbpr))+geom_histogram()
```

```{r}
Data2 %>%
  ggplot(aes(dmdx))+geom_bar()
```

### Checking Correlation

```{r}
Data3<-Data2 %>%
  select(where(is.numeric))
cor.Data3 <- cor(Data3, use = "complete.obs", method="pearson")
head(round(cor.Data3,2))
corrplot(cor.Data3)
```

There is correlation between msbpr and mdbpr also between hba1c and fbs

# Estimation

## Multivariable model without Interaction

Outcome : hba1c

IV : age, msbpr, fbs, hdl, dmdx

```{r}
mod.MLR <- lm (hba1c ~ age + msbpr+ fbs + hdl + dmdx, data=Data2)
summary(mod.MLR)
```

```{r}
tidy(mod.MLR, confin)
```
